% ===========================================================================
% 4. Experiment Methodology
% ===========================================================================
\section{Experiment Methodology}
\label{sec:methodology}

\subsection{Model Under Test}
\label{sec:method-models}

We evaluate \model{GPT-4o-mini} accessed via GitHub Models at
temperature $T=0.7$ with a maximum completion length of 4{,}096 tokens.
GPT-4o-mini is an ``efficient-tier'' model from OpenAI, representing the
class of smaller, cost-effective models increasingly deployed in
agentic applications. Testing a single model enables a focused analysis
of scenario-level vulnerability; multi-model comparison is left to
future work.

\subsection{Experimental Conditions}
\label{sec:method-conditions}

Each scenario is tested under two conditions:

\begin{enumerate}[nosep,leftmargin=*]
  \item \textbf{Baseline}: The agent operates with no defensive
    mitigations. This measures the inherent vulnerability of the
    model to each trap category.

  \item \textbf{Hardened}: All seven mitigation modules
    (\cref{sec:mitigations}) are active, plus a security-hardened
    system prompt suffix instructing the agent to validate sources,
    be suspicious of hidden content, and report anomalies.
\end{enumerate}

\noindent\textbf{Confound note.} The hardened condition simultaneously
changes two variables: mitigation modules and system prompt. We cannot
attribute observed improvements to either factor alone. A factorial
decomposition (prompt-only, modules-only) is planned for future work.

\subsection{Experiment Matrix}
\label{sec:method-matrix}

The experiment comprises:

\begin{equation}
  22 \text{ scenarios} \times 2 \text{ conditions} \times 5 \text{ reps}
  = 220 \text{ experiment cells}
  \label{eq:matrix}
\end{equation}

\noindent Each cell is assigned a deterministic seed
($\text{cellIndex} \times 1337 + \text{rep}$) for reproducible experiment
assignment. Note that seeds control cell assignment metadata only; LLM
outputs remain stochastic at $T=0.7$, with variance captured across the
5 repetitions.

\subsection{Statistical Analysis}
\label{sec:method-stats}

All metrics are aggregated across $n=5$ repetitions per cell. We report:

\begin{itemize}[nosep,leftmargin=*]
  \item \textbf{Central tendency}: Mean trap success rate per scenario.
  \item \textbf{Significance testing}: Wilcoxon signed-rank test
    (non-parametric paired test) for baseline vs.\ hardened
    comparisons~\cite{wilcoxon1945individual}.
  \item \textbf{Effect sizes}: Cohen's $d$ with pooled standard
    deviation, classified as negligible ($|d| < 0.2$), small
    ($0.2 \leq |d| < 0.5$), medium ($0.5 \leq |d| < 0.8$), or
    large ($|d| \geq 0.8$)~\cite{cohen1988statistical}.
  \item \textbf{Multiple comparison correction}: Bonferroni correction
    with $\alpha = 0.05$ divided by 22 simultaneous scenario comparisons,
    yielding $\alpha_{\text{corrected}} = 0.00227$.
\end{itemize}

\paragraph{Statistical power limitation.}
At $n=5$, our design has low statistical power ($<15\%$) to detect
medium effects ($d=0.5$) at the Bonferroni-corrected threshold.
The study is powered only for very large effects ($d \geq 1.5$).
Consequently, \emph{no individual scenario comparison reaches
Bonferroni significance} in our data, and non-significant results
should not be interpreted as evidence of no effect. We report uncorrected
$p$-values alongside Cohen's $d$ and interpret results primarily through
effect sizes rather than null-hypothesis significance testing.

\subsection{Execution Infrastructure}
\label{sec:method-infra}

Experiments are executed using the Bun runtime with 8 parallel workers.
Each cell has a 120-second timeout. Failed and timed-out cells are
recorded with empty metrics and excluded from aggregate statistics.
The full matrix of 220 cells completed in approximately 0.5 compute-hours
via the GitHub Models API.

\subsection{Ethical Considerations}
\label{sec:method-ethics}

All adversarial scenarios are executed in isolated sandbox environments.
No real users, systems, or services are targeted. The A2A agents under
test communicate only within the testbed's local network. We follow
responsible disclosure practices.
