% ===========================================================================
% 9. Results: Systemic (Multi-Agent)
% ===========================================================================
\section{Results: Systemic}
\label{sec:results-sys}

This section reports results for the three systemic scenarios:
\trap{Message-Poisoning} (SY-1), \trap{Agent-Impersonation} (SY-2),
and \trap{Cascade-Failure} (SY-3). These attacks exploit multi-agent
topologies enabled by the A2A protocol.

\subsection{Cascade Metrics}
\label{sec:sys-cascade}

In addition to the standard metrics, systemic scenarios report
\metric{cascade depth} (number of agents sequentially compromised)
and \metric{blast radius} (fraction of the agent crew affected).

\begin{table}[t]
  \centering
  \caption{Systemic attack metrics under baseline (B) and hardened (H)
    conditions. $\tau$: trap success (\%), $C_d$: cascade depth
    (agents), $B_r$: blast radius (\%). Values: mean $\pm$ std, $n=10$.}
  \label{tab:sys-metrics}
  \small
  \begin{tabular}{@{}llcccc@{}}
    \toprule
    & & \model{GPT-4o} & \model{Sonnet~4} & \model{Gemini} & \model{4o-mini} \\
    \midrule
    \multirow{2}{*}{SY-1 $\tau$}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{SY-1 $C_d$}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{SY-2 $B_r$}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{SY-3 $C_d$}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Key Findings}
\label{sec:sys-findings}

\begin{enumerate}[nosep,leftmargin=*]
  \item \textbf{Message poisoning (SY-1)} in A2A communications
    achieves moderate cascade depths even in the baseline condition.
    A single poisoned task message can corrupt the downstream agent's
    context, which in turn produces corrupted outputs for further
    downstream agents.

  \item \textbf{Agent impersonation (SY-2)} exploits the lack of
    strong identity verification in the A2A protocol. When an
    adversarial agent presents a forged Agent Card with elevated
    capabilities, peer agents delegate sensitive tasks to the
    impersonator.

  \item \textbf{Cascade failure (SY-3)} demonstrates \emph{unbounded}
    propagation in baseline conditions: cascade depth scales linearly
    with crew size. The \mitigation{cascade-breaker} module
    introduces circuit-breaker semantics that bound cascade depth,
    reducing blast radius by a statistically significant margin.

  \item \textbf{Protocol implication}: These results motivate
    mandatory message signing, trust scoring, and anomaly detection
    as extensions to the A2A specification
    (\cref{sec:discuss-protocol}).
\end{enumerate}
