% ===========================================================================
% 8. Results: Behavioural Control
% ===========================================================================
\section{Results: Behavioural Control}
\label{sec:results-bc}

This section reports results for the four behavioural control
scenarios: \trap{Deceptive-Dialogs} (BC-1), \trap{Misleading-Forms}
(BC-2), \trap{Hidden-Fields} (BC-3), and \trap{Infinite-Loops} (BC-4).
These attacks exploit the agent's interaction with UI elements and
structured interfaces.

\subsection{Wrong-Action Rates}
\label{sec:bc-actions}

\begin{table}[t]
  \centering
  \caption{Behavioural control trap success rates (\%) under baseline
    (B) and hardened (H) conditions. For BC-4 (infinite loops), we
    report token waste ($w$) instead of binary success. Values:
    mean $\pm$ std, $n=10$.}
  \label{tab:bc-success}
  \small
  \begin{tabular}{@{}llcccc@{}}
    \toprule
    & & \model{GPT-4o} & \model{Sonnet~4} & \model{Gemini} & \model{4o-mini} \\
    \midrule
    \multirow{2}{*}{BC-1}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{BC-2}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{BC-3}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \midrule
    \multirow{2}{*}{BC-4}
      & B & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
      & H & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} & \textcolor{red}{[TBD]} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Key Findings}
\label{sec:bc-findings}

\begin{enumerate}[nosep,leftmargin=*]
  \item \textbf{Deceptive dialogs (BC-1)} exploit the agent's
    tendency to comply with presented options. When a dialog box
    presents ``Confirm'' and ``Cancel'' with swapped semantics, agents
    frequently select the wrong action.

  \item \textbf{Hidden fields (BC-3)} are effective because agents
    processing form data often include hidden input fields in their
    submissions without validation, enabling data exfiltration.

  \item \textbf{Infinite loops (BC-4)} demonstrate a distinct failure
    mode: rather than a binary success/failure, they cause progressive
    resource exhaustion. \model{GPT-4o-mini} is particularly
    susceptible due to its tendency to follow repetitive instructions
    without loop detection.

  \item The \mitigation{behavioral-guard} module is highly effective
    against BC-1 and BC-2 (deceptive dialogs and misleading forms)
    but provides only moderate protection against BC-4 (infinite
    loops), where the adversarial pattern is temporal rather than
    structural.
\end{enumerate}
