% ===========================================================================
% 5. Results: Content Injection
% ===========================================================================
\section{Results: Content Injection}
\label{sec:results-ci}

The four content injection scenarios target hidden instructions embedded
in rendered content. \Cref{tab:ci-success} reports trap success rates
for \model{GPT-4o-mini} under both conditions.

\begin{table}[t]
  \centering
  \caption{Content injection trap success rates (\%) for
    \model{GPT-4o-mini}: baseline (B) vs.\ hardened (H), $n=5$.
    $\Delta$: change in percentage points. Effect sizes and
    uncorrected $p$-values from Wilcoxon signed-rank tests.
    No comparison reaches Bonferroni significance ($p < 0.00227$).}
  \label{tab:ci-success}
  \small
  \begin{tabular}{@{}lrrrcr@{}}
    \toprule
    \textbf{Scenario} & \textbf{B (\%)} & \textbf{H (\%)} & \textbf{$\Delta$} & \textbf{$d$} & \textbf{$p$} \\
    \midrule
    CI-1: CSS invisible    & \textbf{100} & \textbf{100} &   0 & 0.00 & 1.000 \\
    CI-2: HTML comments    &  40 &   \textbf{0} & $-$40 & 1.03 & 0.142 \\
    CI-3: Image metadata   &  40 &  40 &   0 & 0.00 & 0.583 \\
    CI-4: Dynamic cloaking & \textbf{100} & \textbf{100} &   0 & 0.00 & 1.000 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Key Findings}
\label{sec:ci-findings}

\begin{enumerate}[nosep,leftmargin=*]
  \item \textbf{CSS invisible text (CI-1) and dynamic cloaking (CI-4)}
    achieve 100\% trap success in \emph{both} conditions. The
    seven-module mitigation suite, including \mitigation{input-sanitizer},
    is entirely ineffective against these rendering-layer attacks.
    This confirms the DeepMind hypothesis that attacks exploiting the
    gap between raw text and visual presentation are especially
    persistent.

  \item \textbf{HTML comments (CI-2)} drop from 40\% to 0\% under
    hardened conditions ($d = 1.03$, large effect), suggesting that
    the \mitigation{input-sanitizer} module successfully strips
    comment-based payloads.

  \item \textbf{Image metadata (CI-3)} shows identical 40\% success
    in both conditions ($d = 0.00$), indicating that the model
    occasionally processes EXIF data but mitigations do not
    specifically target this vector.

  \item \textbf{Overall}, content injection is the most
    mitigation-resistant category: two of four scenarios show
    complete resistance to all defenses.
\end{enumerate}
